\documentclass[11pt,oneside]{book}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{Per-chapter bibliographies with bibunit}

\usepackage[a4paper]{geometry}

\usepackage[sectionbib]{natbib}
\usepackage{bibunits}
%\defaultbibliographystyle{unsrtnat}  %% For numerical citations remember to pass "numbers" option to natbib
\defaultbibliographystyle{dcu}
\defaultbibliography{sample}


%%% Uncomment if you change the bibliography heading/title
% \renewcommand{\bibname}{References}

%%% Uncomment if you want to include the bibliographies at the end of each chapter in the table of contents.  
% \usepackage[nottoc]{tocbibind}

\begin{document}

\frontmatter

\chapter*{Abstract}
This is \emph{not} a full thesis template! It only demonstrates how to create per-chapter references using the \texttt{bibunits} package with BibTeX. (Do not use with BibLaTeX!)

There are two possible ways to do this. One is by calling \verb|\bibliographyunit[\chapter]| after \verb|\begin{document}|, so that \texttt{bibunits} will automatically treat each chapter as a reference/bibliography unit. (The file \texttt{main.tex} uses this approach.) Another way is to put \verb|\begin{bibunit}...\end{bibunit}| around each chapter, or around arbitrary blocks of text, which may be useful if you need to put the references at the end of each \textit{part} instead of chapter! (This file uses this approach.)

When using \texttt{bibunits}, you may get a warning \verb|I found no \citation commands| if all your chapters are in their own \texttt{.tex} files and there is no \verb|\cite| commands in the main \texttt{.tex} file itself. This warning can be ignored if that's how you intended things to be anyway.

\tableofcontents

\mainmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{First Chapter}

\begin{bibunit}
%% You can use \begin{bibunit}[style] if you need a different bibliography style for this bibunit
\section{Section Heading}
Here's a citation! \citep{latex:companion}

\putbib
%% You can use \pubib[anotherfile] if citations in this bibunit is from anotherfile.bib instead

\end{bibunit}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Second Chapter}

\begin{bibunit}
\section{Section Heading}
Here's another citation! \citep{lshort}

\putbib
\end{bibunit}


\backmatter

%% A list of publications can be created using this approach
\begin{bibunit}
\nocite{lim:etal:kdtei:2016,markdown:overleaf}   % .bib keys of your own publications

\renewcommand{\bibsection}{%
  \chapter*{List of Publications}
  \addcontentsline{toc}{chapter}{List of Publications}
}
\putbib
\end{bibunit}

\end{document}
